\documentclass[12pt]{article}

\usepackage[margin=1.5cm, top=1cm]{geometry}
\usepackage{amsmath, amsfonts}
\usepackage[version=4]{mhchem}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{listing}
\usepackage{wrapfig}
\usepackage{graphbox}

\newcommand*{\figref}[2][]{%
  \hyperref[{fig:#2}]{%
    Figure~\ref*{fig:#2}%
    \ifx\\#1\\%
    \else
      \,#1%
    \fi
  }%
}

\begin{document}

\pagenumbering{roman}

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
 
        \textbf{Characterizing a Low Energy Electron Gun for use in Inverse Photoemission Spectroscopy}
             
        \vspace{1.5cm}
 
        \textbf{Michael Bouliane}
 
        \vfill
             
        A report submitted for partial fulfillment of the requirements of Phys 437B

        Source files and full sized images available at: \url{https://github.com/m-bouliane/Phys-437B}
             
        \vspace{0.8cm}
             
        Department of Physics and Astronomy\\
        University of Waterloo\\
        \today\\
             
    \end{center}
\end{titlepage}

\begin{abstract}
Inverse photoemission spectroscopy (IPES) provides a means to map the unoccupied electronic states of materials which are inaccessible to other techniques which map 
occupied electronic states. The coupling of electrons in an emitted beam to these unoccupied states can release detectable photons through the process 
of inverse photoemission. Unfortunately inverse photoemission spectrometers are not commercially available, and thus have to be built up from 
scratch. In order to obtain quality IPES results, a spectrometer has strict requirements for its electron source, photodetectors, and sample quality. 
This means that upon completing the construction of a spectrometer much work needs to be done to characterize its performance to ensure it is 
capable of collecting good data. 

Having previously focused on the photodetection capabilities of our spectrometer for Phys 437A, this report details our efforts to characterize our
electron source. Inverse photoemission requires low energy electrons, in a well collimated beam with a high brightness and small spot size. Space 
charge effects make this a very difficult task, which thankfully commercially available systems have solved for us. The task is to therefore find 
the appropriate operating conditions of the electron source which meet the above requirements, yet another difficult task due to the large parameter space
of the optimization problem.

By measuring the beam width and brightness at a set of manufacturer recommended parameters, we found a beam which was unfit for IPES applications. 
Space charge effects were found to be the limiting factor of this beam, so changes were made when exploring parameter space to minimize its impacts. 
Eventually a beam with a spot size of $2.033\pm0.014$mm and divergence angle of $4.15\pm0.50^\circ$ was obtained. The momentum resolution of the beam 
was then calculated to be $(1.07\pm0.13)\times10^9\mathrm{m}^{-1}$, an order of magnitude less than the size of copper's first brillouin zone. Our 
efforts to produce a beam fit for inverse photoemission spectroscopy were an overwhelming success, agreeing strongly with the results published by 
groups working with similar systems. 

Finally an angle resolved inverse photoemission experiment was performed on Cu(111), which did not at all meet expectations. We determined that 
this was due to sample quality and not the electron beam or photodetectors. Future tests on Cu(111) will be performed in an attempt to obtain results 
which align with those reported in literature, giving us vital insight into our spectrometer's overall performance.
    
\end{abstract}

\clearpage

\tableofcontents
\clearpage

\listoffigures
\listoftables

\clearpage

\pagenumbering{arabic}

\input{Introduction.tex}
\input{Experimental Design.tex}
\input{Results.tex}
\input{Discussion.tex}

\bibliography{citations}
\bibliographystyle{abbrv}

\end{document}